Balsa: A Compact Line Notation Based on SMILES

### 2022-07-02 manuscript.tex
Clarifies caption on atom parity w/ virtual hydrogen.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{atom-parity-suppressed-hydrogen.pdf}
    \caption{Atom parity with one suppressed hydrogen. The central atom (cyan) has a suppressed hydrogen. In this case, the root atom (r) is regarded as the first child and analysis continues as before.}
    \label{fig:atom-parity-suppressed-hydrogen}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{atom-parity-suppressed-hydrogen.pdf}
    \caption{Atom parity with one virtual hydrogen. The central atom (cyan) has a virtual hydrogen (left). In this case, the virtual hydrogen assumes the role of root atom (right). The former root atom (r) then assumes the role of the first child,  and analysis continues as before.}
    \label{fig:atom-parity-suppressed-hydrogen}
\end{figure}
